\begin{description}[itemsep=15pt]

    \item[Software Engineer, \href{http://capside.com}{CAPSiDE}] \hfill

        \emph{IT services and infraestructure. Development department.}

        Barcelona, Jan.\ 2016 - Present

        Perl, Node.js, AngularJS, Vue.js, Elasticsearch, AWS, Azure, Ansible, Docker

        \begin{itemize}[itemsep=0pt]
            \item Promoted the adoption of software design concepts such as SOLID principles, design patterns, architectures and Domain-Driven Design.
            \item Also promoted software quality and maintainability principles such as code readability, refactoring, extensive testing and code reviews.
            \item Performed internal trainings in order to introduce some of the previous concepts to the team.
            \item Defined a frontend code architecture that separates application and framework-coupled logic, allowing the application to easily adapt for the fast-changing JavaScript ecosystem.
            \item Optimized the development environments so they were easier to use, more automated and consistent with production.
            \item Participated in the development of web applications that manage AWS and Azure cloud infraestructures.
        \end{itemize}
\newpage

    \item[Adjunct Lecturer in Web Projects, \href{http://www.salleurl.edu}{La Salle Campus}] \hfill

        \emph{Engineering university. Computer Engineering department.}

        Barcelona, Oct.\ 2015 - Feb.\ 2016

        \begin{itemize}[itemsep=0pt]
%            \item Teached and evaluated engineering students in 2nd year subjects Web Projects and Web Programming Environments.
            \item Introduced students to web development using HTML5, CSS3, JavaScript and PHP.
            \item Guided students in the setup and use of a development environment using Vagrant, Apache, MySQL and Git.
            \item Teached and evaluated those fields for the Web Projects and Web Programming Environments subjects.
        \end{itemize}

    \item[Teaching Assistant in Web Projects, \href{http://www.salleurl.edu}{La Salle Campus}] \hfill % \\ noenter

        \emph{Engineering university. Computer Engineering department.}

        Barcelona, Feb.\ 2013 - Sep.\ 2013 / Feb.\ 2014 - Sep.\ 2014 / Feb.\ 2015 - Sep.\ 2015

        \begin{itemize}[itemsep=0pt]
%            \item Guided and evaluated engineering students in the practical load of 3rd year subject Web Projects.
            \item Introduced students to web development using Apache, MySQL, PHP frameworks and version control.
            \item Guided and evaluated the development of a web application as part of their group project.
            \item Participated in the drafting of subject materials.
        \end{itemize}

    \item[Intern, \href{http://www.t-systems.es}{T-Systems Iberia}] \hfill

        \emph{IT services and consulting. Automation \& Tools department.}

        Barcelona, May 2013 - May 2014 / Oct.\ 2014 - Jun.\ 2015

        PHP, Zend Framework, JavaScript, Bash, Pentaho, IBM Tivoli

        \begin{itemize}[itemsep=0pt]
            \item Developed cross-browser intranet web applications that implied a noticeable performance improvement in some of the company departments.
            \item Reduced the time needed to analyze the servers status and draft monthly reports on an estimation of 12 hours per month.
            \item Managed monitoring and data integration tools.
            \item Participated in the automation of monitoring agent installations through the development of shell scripts.
        \end{itemize}

    \item[Teaching Assistant in Computer Programming 1, \href{http://www.salleurl.edu}{La Salle Campus}] \hfill

        \emph{Engineering university. Computer Engineering department.}

        Barcelona, Sep.\ 2012 - Jun.\ 2013
        \begin{itemize}[itemsep=0pt]
%            \item Guided engineering students in the practical load of 1st year subject Computer Programming 1.
            \item Introduced students to the basics of computer programming using C language.
            \item Introduced students to the use of the Linux command-line.
            \item Helped students with the development in C of three small games, executed through command-line or graphical interface.
        \end{itemize}

%    \item[Technical Assistant, \href{http://www.itc2.com}{ITC-2}] \hfill
%
%        \emph{Systems engineering, telecommunications and electric power distribution. Documentation department.}
%
%        Barcelona, Jul.\ 2009 - Aug.\ 2009
%        \begin{itemize}[itemsep=0pt]
%            \item Managed and redacted documentation for electrical network works.
%        \end{itemize}

%    \item[Technical Assistant, \href{http://sparkiberica.com}{Spark Ibérica}] \hfill
%
%        \emph{Electrical installations and telecommunications. Cartography department.}
%
%        Barcelona, Jul.\ 2008 - Aug.\ 2008
%        \begin{itemize}[itemsep=0pt]
%            \item Digitalized documentation about the electric power distribution.
%            \item Verified and updated cartographic documentation.
%        \end{itemize}

\end{description}
